### 2017-02-27 2017mergingmerges/section/05-Evaluation.tex
Start opt. section

% -----------------------------------------------------------------------------
\subsection{Optimisation}
\label{s:Optimisation}
After the algorithm has completed fusing both processes it may be possible to eliminate redundant @jump@, depending on how the affected variables are used by other instructions.

\TODO{Discuss combining jump instructions here. Use this to motivate the need for drop instructions.}

>>>>

% -----------------------------------------------------------------------------
\subsection{Optimisation with Drop Instructions}
\label{s:Optimisation}
After we have fused two processes together, it may be possible to simplify the result before fusing in a third. Consider the result of fusing @group@ and @merge@ which we saw back in Fig.\ref{fig:Process:Fused}. At labels @F1@ and @F2@ are @jump@ instructions, where the first passes control to the second. The update expressions attached to these instructions are also non-interferring, which means we can safely combine these consecutive @jump@ instructions into a single @jump@ to @F4@. There are also @jump@ instructions like the one at @F5@ which have no associated update expressions, and thus can be eliminated completely. We can also perform constant propagation, which in this case would allow us to eliminate the first @case@ instruction.

Minimising the number of states in intermediate processes has a follow-on effect in that the final fused result has a lower number of states. Provided we do not change the order of instructions that do not require synchronization with other processes, meaning @pull@ @push@ or @drop@, the fusability of the overall process network will not be affected.

Another useful optimization is to notice that in some cases, when a heap variable is updated it is always assigned the value of another variable. In Fig.\ref{fig:Process:Fused}, the @v@ and @x1@ variables are only ever assigned the value of @b1@, and @b1@ itself is only ever loaded via a @pull@ instruction. Remember from \S\ref{s:Fusion:FusingPulls} that the variable @b1@ is the stream buffer variable. Values pulled from stream @sIn1@ are first stored in @b1@ before being copied to @v@ and @x1@. When the two processes to be fused share a common input stream, use of stream buffer variable allows one process to continue using the value that was last pulled from the stream, while the other moves onto the next one.

When the two processes to be fused are able to accept the next variable from the stream at the same time, there is no need for the separate stream buffer variable. In this case we can perform a copy-propagation optimisation, replacing all occurrences of @v@ and @x1@ with the single variable @b1@.
